Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
squeeze abstract

\begin{abstract}
This work presents a sound and automated approach to synthesise 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space describing 
the evolution of the physical variables of the system.  The approach is divided 
in two main parts, brought together by a counter-example guided inductive 
synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
that stabilises the system; then, we verify its potential safety by means of either 
of the following approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  
further, if the above step fails, we loop back and invoke a CEGIS call 
to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
to safety. The approach is proven sound by accounting for errors due to the digitalisation 
of signals that are manipulated by the controller block.  
The proposed synthesis approaches and a developed tool are evaluated considering 
a set of intricate physical plant models taken from the digital control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesize 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space and accounting 
for errors due to the digitalization of signals that are manipulated by the 
controller block. The approach is divided in two main parts, brought together 
by a counter-example guided inductive synthesis (CEGIS) loop, as follows. 
First, we devise a static feedback controller that stabilizes the system; 
then, we verify its potential safety by means of either of the following 
approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  further, if the 
above step fails, we loop back and invoke a CEGIS call to seek alternative 
stabilizing feedback, benefiting from the obtained counterexamples 
to safety. Both approaches are able to efficiently synthesize stable and 
safe controllers considering a set of intricate physical plant models taken 
from the digital control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}
